---
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Import Data, echo = FALSE, warning = FALSE, message = FALSE}
'%!in%' <- function(x,y)!('%in%'(x,y))
inc_sites <- c("NETWORK","MSM","MSH-MSDFP","ONCOLOGY","MSW","MSBI","MSUS","MSH- AMBULATORY CARE","MSDD")


scheduling_data_raw <- as.data.frame(readRDS("/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/historical_data_11.2.2022.rds")) %>%
  filter(!is.na(Campus)) %>%
  filter(Campus %in% c("NETWORK","MSM","MSH-MSDFP","ONCOLOGY","MSW","MSBI","MSUS","MSH- AMBULATORY CARE","MSDD"))


date_start <- as.Date("2022-01-01", format="%Y-%m-%d")
date_end <- as.Date("2022-10-31", format="%Y-%m-%d")

```


```{r Scheduling Metrics, echo = FALSE, warning = FALSE, message = FALSE}

# Scheduling Data Processing ---------------------------------------------------
scheduling_data_raw <- scheduling_data_raw %>%
  mutate(Visit.Method  = case_when(Visit.Method == "IN PERSON" ~ 'IN PERSON',TRUE ~ 'TELEHEALTH'),
         New.PT2 = case_when(New.PT2 == "New" ~ 'New', TRUE ~ 'Established'),
         New.PT3 = case_when(New.PT3 == "TRUE" ~ 'New',TRUE ~ 'Established')) %>%
   mutate(Appt.Made.DateYear = as.Date(Appt.Made.DTTM, format="%Y-%m-%d"),
          Appt.Made.MonthYear = format(as.Date(Appt.Made.DTTM, format="%m/%d/%Y"), "%Y-%m"),
          Appt.Made.Year = format(as.Date(Appt.Made.DTTM, format="%m/%d/%Y"), "%Y"),
          Appt.Made.WeekNum = as.numeric(strftime(Appt.Made.DTTM, format = "%V")))


# Volume by Site and Specialty -------------------------------------------------
vol_site_specialty <- scheduling_data_raw %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  mutate(Appt.Status = case_when(Appt.Status == "Canceled" & Appt.DateYear == as.Date(Appt.Cancel.DTTM, format="%Y-%m-%d") ~ "Same-Day Canceled",
                                 TRUE ~ Appt.Status)) %>%
  group_by(Campus, Campus.Specialty, Appt.Status) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = Appt.Status,
              values_from = total,
              values_fill = 0) 

vol_site_specialty$Total <- rowSums(vol_site_specialty[,3:length(vol_site_specialty)] )
vol_site_specialty <- vol_site_specialty %>%
  mutate(`No Show Rate` = percent((`No Show` + `Same-Day Canceled`) / (Arrived + `No Show` + `Same-Day Canceled`),0),
         `No Show Plus Rate` = percent((`No Show` + `Same-Day Canceled`) / Total,0))
  
# Volume by Specialty ----------------------------------------------------------
vol_specialty <- scheduling_data_raw %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= date_end) %>%
  mutate(Appt.Status = case_when(Appt.Status == "Canceled" & Appt.DateYear == as.Date(Appt.Cancel.DTTM, format="%Y-%m-%d") ~ "Same-Day Canceled",
                                 TRUE ~ Appt.Status)) %>%
  group_by(Campus.Specialty, Appt.Status) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = Appt.Status,
              values_from = total,
              values_fill = 0) 

vol_specialty$Total <- rowSums(vol_specialty[,3:length(vol_specialty)] )
vol_specialty <- vol_specialty %>%
  mutate(`No Show Rate` = percent((`No Show` + `Same-Day Canceled`) / (Arrived + `No Show` + `Same-Day Canceled`),0),
         `No Show Plus Rate` = percent((`No Show` + `Same-Day Canceled`) / Total,0))

# Percent of New Patients Scheduled Within 14 Days by Site and Specialty -------
new14_perc_site_specialty <- scheduling_data_raw %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  filter(Wait.Time >= 0) %>%
  mutate(Wait.Time = as.numeric(Wait.Time)) %>%
  mutate(within.14 = ifelse(Wait.Time <= 14, "Yes","No")) %>%
  group_by(Campus, Campus.Specialty, within.14) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = within.14,
              values_from = count,
              values_fill = 0) %>%
  mutate(total = Yes + No,
         new_14days = round((Yes/(total))*100))

# Percent of New Patients Scheduled Within 14 Days by Specialty ----------------
new14_perc_specialty <- scheduling_data_raw %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  filter(Wait.Time >= 0) %>%
  mutate(Wait.Time = as.numeric(Wait.Time)) %>%
  mutate(within.14 = ifelse(Wait.Time <= 14, "Yes","No")) %>%
  group_by(Campus.Specialty, within.14) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = within.14,
              values_from = count,
              values_fill = 0) %>%
  mutate(total = Yes + No,
         new_14days = round((Yes/(total))*100))

# New Wait Time by Site and Specialty ------------------------------------------
new_wait_site_specialty <- scheduling_data_raw %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  filter(Wait.Time >= 0) %>%
  mutate(Wait.Time = as.numeric(Wait.Time)) %>%
  group_by(Campus, Campus.Specialty) %>%
  summarise(waitTime = round(median(Wait.Time, na.rm = TRUE)))

# New Wait Time by Specialty ---------------------------------------------------
new_wait_specialty <- scheduling_data_raw %>%
  filter(Appt.Made.DateYear >= date_start & Appt.Made.DateYear <= date_end) %>%
  filter(New.PT2 == "New") %>%
  filter(Wait.Time >= 0) %>%
  mutate(Wait.Time = as.numeric(Wait.Time)) %>%
  group_by(Campus.Specialty) %>%
  summarise(waitTime = round(median(Wait.Time, na.rm = TRUE)))

```


```{r Provider Mappping, echo = FALSE, warning = FALSE, message = FALSE}

provider_mapping <- scheduling_data_raw %>%
  group_by(Campus, Campus.Specialty, Provider, NPI) %>%
  summarise(total = n())

# write.xlsx(provider_mapping , file = "/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/provider_mapping .xlsx")

```


```{r Merged Data, echo = FALSE, warning = FALSE, message = FALSE}

site_specialty_merge <- merge(vol_site_specialty %>% dplyr::select(Campus, Campus.Specialty, Total, Arrived, `No Show`, `Same-Day Canceled`, `No Show Rate`, `No Show Plus Rate`),
                    new_wait_site_specialty)
site_specialty_merge <- merge(site_specialty_merge, new14_perc_site_specialty %>% dplyr::select(Campus, Campus.Specialty, new_14days))


specialty_merge <- merge(vol_specialty %>% dplyr::select(Campus.Specialty, Total, Arrived, `No Show`, `Same-Day Canceled`, `No Show Rate`, `No Show Plus Rate`),
                    new_wait_specialty)
specialty_merge <- merge(specialty_merge, new14_perc_specialty %>% dplyr::select(Campus.Specialty, new_14days))

require(openxlsx)
list_of_datasets <- list("Site and Specialty" = site_specialty_merge, "Specialty" = specialty_merge)
write.xlsx(list_of_datasets, file = "/SharedDrive/deans/Presidents/SixSigma/Individual Folders/Current Employees/Engineers/So Youn Kweon/server-upload/access-center-wait-time_JanOct22.xlsx")

```


```{r Booked and Filled Rate Data, echo = FALSE, warning = FALSE, message = FALSE}

# con <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
# slot_data <- tbl(con, in_schema("VILLEA04", "Y_DM_BOOKED_FILLED_RATE"))
# slot_data_raw <- slot_data %>%
#   filter(CONTACT_DATE >= as.Date("2022-01-01") & CONTACT_DATE <= as.Date("2022-05-31")) %>%
#   group_by(CONTACT_DATE, DEPARTMENT_NAME, DEPARTMENT_ID, PROVIDER_NAME, 
#            SLOT_BEGIN_TIME, NUM_APTS_SCHEDULED, SLOT_LENGTH,
#            AVAIL_MINUTES, BOOKED_MINUTES, ARRIVED_MINUTES, CANCELED_MINUTES, NOSHOW_MINUTES, LEFTWOBEINGSEEN_MINUTES,
#            AVAIL_SLOTS, BOOKED_SLOTS, ARRIVED_SLOTS, CANCELED_SLOTS, NOSHOW_SLOTS, LEFTWOBEINGSEEN_SLOTS,
#            ORG_REG_OPENINGS, ORG_OVBK_OPENINGS, PRIVATE_YN, DAY_UNAVAIL_YN, TIME_UNAVAIL_YN, DAY_HELD_YN, TIME_HELD_YN,
#            OUTSIDE_TEMPLATE_YN, VISIT_PROV_STAFF_RESOURCE_C) %>%
#   summarise(total = n()) %>%
#   collect()
# 
# 
# # Slot Date Processing ---------------------------------------------------------
# slot_data_raw <- slot_data_raw %>%
#   mutate(Appt.DateYear = as.Date(SLOT_BEGIN_TIME, format="%Y-%m-%d"),
#          Appt.MonthYear = format(as.Date(SLOT_BEGIN_TIME, format="%Y-%m-%d %H:%M:%S"), "%Y-%m"),
#          Appt.Year = format(as.Date(Appt.DTTM, format="%Y-%m-%d %H:%M:%S"), "%Y"),
#          Resource = ifelse(VISIT_PROV_STAFF_RESOURCE_C == 1, "Provider", "Resource"))


```

